Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-08-20 paper/paper.tex
feat(paper): Minor revisions

The four key phases are the configure phase, the build phase, the install phase, and the check phase.
During the configure phase, the build system is configured.
The build phase defines the build steps, such as calling \texttt{make} or \texttt{cargo build}.
Afterwards, the install phase copies the results into the output directory.
The check phase can be enabled to run any tests.
Most phases have a pre and post step, which can be uses to make adjustments.

@@

Despite encountering challenges in packaging the numerous software tools, we were able to observe the adaptability of the Nix package manager.
Our results indicate that, in general, Nix is a suitable solution for reproducing software environments.

>>>>

For building packages, the four key phases are the \texttt{configurePhase}, the \texttt{buildPhase}, the \texttt{installPhase} and the \texttt{checkPhase}.
During the \texttt{configurePhase}, the build system is configured.
The \texttt{buildPhase} defines the build steps, such as calling \texttt{make} or \texttt{cargo build}.
Afterwards, the \texttt{installPhase} copies the results into the output directory.
The \texttt{checkPhase} can be enabled to run any tests.
Most phases have a pre and post step, which can be uses to make adjustments.

@@

Despite encountering challenges in packaging the numerous software tools, we were able to observe the adaptability of the Nix package manager.
Our results indicate that, in general, Nix is a suitable solution for reproducing software environments and a viable solution to package management in a scientific domain.
